%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Mauricio Perez} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:713-385-8816}{713-385-8816}
    $|$
   \faAt \hspace{.5pt} \href{mailto:mauri\_guzman\_\@outlook.com}{mauri\_guzman\_\@outlook.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/mauricio-perez-guzman/}{LinkedIn: https://www.linkedin.com/in/mauricio-perez-guzman/ } \newline
    \faGithub \hspace{.5pt} \href{https://github.com/mauri1738guzman}{GitHub: https://github.com/mauri1738guzman }
  
    \faMapMarker \hspace{.5pt} {Houston, TX}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Houston
      % \normalfont{(Admission rate: 0.09\%)}
      }{Houston, TX}
      {B.Sc. in Computer Science;   \textbf{GPA: 3.6/4.00}}{Jan 2020 \textbf{--} May 2023}
      {Minor Degree in Mathematics;
      \textbf{GPA: 3.60/4.00}}{Oct 2020 \textbf{--} May 2023}
      
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ C/C++, Java, VBA, Python, Raspberry Pi,  .NetFramework, Machine Learning, Virtualization, ASP.NET} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ MySQL, Virtual Box,OpenGL, Unity, Linux } \vspace{3pt}
        
        \textbf{Libraries:}{ OpenCV, Scikit-Learn, PyTorch, Keras, TensorFlow, NumPy, Pandas, Matplotlib, Seaborn} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Hewlett Packard Enterprise}{Houston, TX}
{Data Analyst}{2022 -- 2023}
\resumeItemListStart
\resumeItem{Research project conducted in a team, using Python to analyze vocal frequencies of patients tested for Parkinson’s Disease. Cleaned up data, removed redundant and artificial data. Debugged code for successful runs.}
\resumeItem{Collaborated using Google Colab, presented quarterly to higher-ups, and employed test models such as SVM and MLP (2 Hidden Layers). Conclusions confirmed evidence for Parkinson’s disease based on certain frequencies.}
\resumeItemListEnd

\resumeSubheading
{ARMY National Guard}{San Antonio}
{Blackhawk Mechanic}{Oct 2020 -- Present}
\resumeItemListStart
\resumeItem{Enlisted for 6 months of training, maintaining military standards daily, including intense workouts and fast-paced group collaboration courses.}
\resumeItem{Trusted with military weapons 24/7, learned helicopter mechanics in another state, and used security clearance-only software.}
\resumeItem{Used KVM Linux Ubuntu and VirtualBox on Windows for saved states, allowing specific access to particular apps at certain updates.}
\resumeItemListEnd

\resumeSubheading
{Kids in Action}{Houston, TX}
{Software Developer (Javascript/PHP)}{May 2017 -- 2020}
\resumeItemListStart
\resumeItem{Used Windows and Linux kernel to save files locally, tested using APACHE, and stored in private GITHUB. Later moved to Azure.}
\resumeItem{Established successful hotspots, maintained expensive equipment, and reduced replacement costs.}
\resumeItem{Remodeled the company site using PHP, HTML, CSS, and Javascript, along with mySQL. Used SEO standards, Cloudflare, and Siteground for hosting and security.}
\resumeItem{Created a C Code server and messaging systems for synchronized communication using TCP connection and threads.}
\resumeItem{Debugged code for initial start and everyday maintenance, especially when working with cloud infrastructure and cloud computing.}
\resumeItem{Implemented a communication system using computers in all rooms of the building for better facility-wide communication.}
\resumeItem{Collaborated with bosses to implement the OS Server/Client project to meet the needs of the business.}
\resumeItemListEnd

\resumeSubHeadingListEnd

   


%----------- RESEARCH EXPERIENCE -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Python Interpreter using C++}{Stuttgart, Baden\textbf{-}Houston, TX}
      {Undergraduate Work}{Jun 2022 \textbf{--} May 2023, Senior Project}
        \resumeItemListStart
           \resumeItem{Using Object Oriented Programming, created an interpreter to compile Python files. Successfully tested cases, including arithmetic, keywords, definitions, and loops.}
            \resumeItem{Utilized Visual Studio 2022 to create a compiler with .cpp and .hpp files.}
            \resumeItem{Applied Linux bash commands to rigorously test all cases.}
        \resumeItemListEnd
    
    \vspace{14pt}
    
    \resumeSubheading
      {Library Database Management System, University of Houston}{Houston, TX}
      {Undergraduate Work}{Jan 2023 \textbf{--} May 2023, Part-time}
       \resumeItemListStart
            \resumeItem{Created a fully functioning library management system using SQL, PHP, Javascript, HTML, and CSS.}
            \resumeItem{Deployed files on Azure Cloud and maintained a GitHub repository for backup.}
            \resumeItem{Utilized XAMPP (APACHE) for local file handling.}
            \resumeItem{Leveraged Git for version control, enabling efficient collaboration through cloning, branching, and pushing files.}
            \resumeItem{Delivered a group presentation covering triggers, assertions, and system schema. Followed Agile Development steps and documented the implementation and adherence to a software design pattern.}
        \resumeItemListEnd


     \resumeSubheading
      {Data Science Income Project, University of Houston}{Houston, TX}
      {Undergraduate Work}{Aug 2022 \textbf{--} Dec 2022, Part-time}
      \resumeItemListStart
            \resumeItem{Conducted a data science project using Python and Anaconda to analyze factors contributing to income levels.}
            \resumeItem{Utilized libraries such as sklearn and seaborn to conclude that a male aged 25-30, Caucasian, working in the corporate sector was most likely to earn over \$50,000.}

            \resumeItem{Explored other factors contributing to salary variations, providing valuable insights for real-life scenarios.}
        \resumeItemListEnd

    \resumeSubheading
        {Arduino Uno, University of Houston}{Houston, TX}
      {Undergraduate Work}{Aug 2022 \textbf{--} Dec 2022, Part-time}
        \resumeItemListStart
        \resumeItem{Dancing Lights (6 months): Developed an Arduino IDE-based device featuring dancing lights triggered by sound, implemented during Christmas.}
        \resumeItem{AC UNIT (6 months): Created a climate control system using Arduino IDE with an LCD screen displaying temperature and a fan activated based on temperature readings.}
        \resumeItemListEnd
                
  \resumeSubHeadingListEnd
    

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Cum Laude:}{ Awarded to Bachelor alumni who have graduated with a GPA greater than or equal to 3.50 byUniversity of Houston. (Jul 2023)} \\ \vspace{3pt}

    
        \textbf{Deans List:}{ Ranked 3.50 in 12 or more semester hour classes (May 2023)} \\ \vspace{3pt}
        
    
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------


%----------- REFERENCES -----------

\section{References}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \item{References available upon request.}
  \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
